Chr11 hotspot analyses

### 2019-07-09 analysis/paper/Chr11-hclusterings.Rmd
updated Rmd files

---
title: "Chr7 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 7
run_num <- 9911
hot_mid <- 46
keller_mediator <- "Fam83e"
library(hotspots)
```

@@

```{r}
dataset.islet.rnaseq$lod.peaks %>%
  filter(chrom == hot_chr, pos <= hot_upper, pos >= hot_lower) %>%
  left_join(y = dataset.islet.rnaseq$annots, by = c("annot.id" = "gene_id")) %>%
  filter(!duplicated(annot.id)) %>%
  filter(lod >= 7.18)
```

@@

```{r define_dri}
# need the index of the peak for every nonlocal trait
indices <- nonlocal_annot %>%
  mutate(marker_index = purrr::map_int(.x = marker.id, .f = function(x){which(names(map[[as.character(hot_chr)]]) == x)})) %>%
  select(marker_index) %>%
  unlist() %>%
  as.integer()
```

@@

```{r tabulate, message=FALSE, warning = FALSE}
tib <- out %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  mutate(local_gene_id = rep(colnames(hot_local), each = nnonlocal), nonlocal_gene_id = rep(colnames(hot_nonlocal), times = nlocal)) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

@@

```{r read_pleio_results}
pleio_file <- paste0("_cache/Chr", hot_chr, "_pleio.rds")
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r plot_all}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05)
plotly::ggplotly(p)

@@

```{r, plotly_by_local, fig.height=ceiling(nlocal / 2), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

```{r, plotly_by_nonlocal, fig.height=ceiling(nnonlocal / 4), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ nonlocal_symbol, ncol = 4, nrow = ceiling(nnonlocal / 4)) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

@@

```{r define_foo}
foo <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) 
```

```{r add_local_peak_positions}
foo %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  rename(local_peak_pos = pos, local_peak_lod = lod) %>%
  select(- marker.id, - chrom, - strand, - biotype, - local_tx) %>%
  filter(local_peak_pos < hot_upper, local_peak_pos > hot_lower)

@@

```{r}
foo %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  rename(local_peak_pos = pos, local_peak_lod = lod) %>%
  select(- marker.id, - chrom, - strand, - biotype, - local_tx) %>%
  filter(local_peak_pos < hot_upper, local_peak_pos > hot_lower) %>%
  select(middle) %>% unlist() %>% range()

@@

```{r, hclust_pleio_stats}
bar <- foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod) %>%
hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
```

@@

```{r heat_pleio_stats, fig.height=4, fig.width = 6}
foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r heat_lod_diff0}
foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  mutate(lod_diff = lod_diff * (lod_diff > 0)) %>%
hotspots::tibble_to_matrix() %>%
  t() %>%
  gplots::heatmap.2(cexRow = 0.1, cexCol = 0.1, col = hmcol, trace = "none")
```

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r define_hc_objects}
hc_lod_diff <- foo %>%
  select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
hc_pleio <- foo %>%
  select(nonlocal_gene_id, local_gene_id, pleiotropy_lod) %>%
  hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
```

@@

```{r make_mylist}
med_vals <- 2 * (1:5)
pleio_vals <- 2 * (2:5)
mylist <- list()
for(i in 1:length(med_vals)){
  my_other_list <- list()
  for (j in 1:length(pleio_vals)){
    uniq_cts_nonlocal <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(nonlocal_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_nonlocal_gene_id = n)
    uniq_cts <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      select(local_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_local_gene_id = n) %>%
      left_join(uniq_cts_nonlocal, by = c("pleio", "med"))

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- paste0("_cache/Chr", hot_chr, "_pleio_local.rds")
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds")
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

@@

```{r}
local_annot3 <- local_annot2 %>%
  select(annot.id, symbol)
local_pleio <- mylist_local %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(local_annot3, by = c("gene1_id" = "annot.id")) %>%
  rename(gene1_symbol = symbol) %>%
  left_join(local_annot3, by = c("gene2_id" = "annot.id")) %>%
  rename(gene2_symbol = symbol)

nonlocal_annot3 <- nonlocal_annot %>%
  select(annot.id, symbol)
nonlocal_pleio <- mylist_nonlocal %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(nonlocal_annot3, by = c("gene1_id" = "annot.id")) %>%
  rename(gene1_symbol = symbol) %>%
  left_join(nonlocal_annot3, by = c("gene2_id" = "annot.id")) %>%
  rename(gene2_symbol = symbol)

@@

```{r}
pleio_results_mat <- foo %>%
  select(local_gene_id, nonlocal_gene_id, pleiotropy_lod, local_symbol, nonlocal_symbol) %>%
  rename(gene1_id = local_gene_id, 
         gene2_id = nonlocal_gene_id, 
         gene1_symbol = local_symbol,
         gene2_symbol = nonlocal_symbol
         ) %>%
  bind_rows(local_pleio, nonlocal_pleio) %>%
  hotspots::tibble_to_matrix(symmetric = TRUE)
```

@@

```{r heatmap.2}
pleio_mat <- foo %>%
  tibble_to_matrix() %>%
  t()
ld <- bar$lod_diff
idx1 <- match(x = bar$nonlocal_symbol, table = rownames(pleio_mat))
idx <- 1 + floor((ld * (ld > 0))[idx1])
cols[idx] -> indexed_colors
ic2 <- 1 + (ld[idx1] > mediation_threshold)
#indexed_colors[is.na(indexed_colors)] <- cols[8]
gplots::heatmap.2(pleio_mat, 
                  trace="none", 
                  #RowSideColors = indexed_colors, 
                  RowSideColors = c("red", "green")[ic2],
                  col=hmcol,
                  cexRow = 0.5,
                  cexCol = 0.5
                  )
```

```{r}
d3heatmap::d3heatmap(t(pleio_mat) <= 4, cexRow = 0.2, cexCol = 0.3)
```

```{r}
gplots::heatmap.2(t(pleio_mat), 
                  trace="none", 
                  #RowSideColors = indexed_colors, 
                  ColSideColors = c("red", "green")[ic2],
                  col=hmcol,
                  cexRow = 0.5,
                  cexCol = 0.5
                  )

@@

```{r define_color}
hmcol <- colorRampPalette(brewer.pal(9, "GnBu"))(100)
heatmap.2(foomat, 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, cexRow = 0.4
      )

@@

```{r, loddiff_clust}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff as the stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, 
          cexRow = 0.4
      )

```{r, loddiffprop_clust}
foo %>%
  select(1, 2, 5) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix() %>%
  heatmap.2( 
          #labCol=tissue,
          trace="none", 
          #ColSideColors=cols, 
          col=hmcol,
          cexCol = 0.2, cexRow = 0.4
      )

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) %>%
    d3heatmap()
```

```{r}
foo %>%
  select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix() %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

@@

```{r}
bccc_out<- biclust(pleio_mat, method = BCCC())
c1 <- bicluster(pleio_mat, bccc_out, number = 1)
d3heatmap(c1$Bicluster1, "none", Rowv = FALSE, cexRow = 0.3, cexCol = 0.3)
```

```{r}
d3heatmap(c1$Bicluster1, cexRow = 0.3, cexCol = 0.3)

@@

```{r}
# subset to get nonlocals that aren't mediated by Hnf4a
# first, get symbols for nonlocals that aren't mediated by Hnf4a
pmat <- bar %>%
  filter(lod_diff <= mediation_threshold) %>%
  dplyr::select(nonlocal_symbol) %>%
  left_join(foo) %>%
  tibble_to_matrix()
dim(pmat)
```

```{r d3heat}
d3heatmap(pmat, cexRow = 0.3, cexCol = 0.3)
```
```{r heat_binary}
hc1 <- hclust(dist(pmat))
plot(hc1, cex = 0.3)
hc2 <- hclust(dist(t(pmat)))
plot(hc2, cex = 0.3)
pmat %>%
  dist() %>%
  hclust()

@@

```{r d3heat_logical}
d3heatmap(pmat > pleiotropy_threshold, cexRow = 0.3, cexCol = 0.3)
```

```{r}
dim(pmat)
length(hc1$order)
d3heatmap(pmat[hc1$order, hc2$order] > pleiotropy_threshold, 
          Rowv = FALSE, 
          Colv = FALSE, 
          cexRow = 0.3, 
          cexCol = 0.3)
d3heatmap(pmat[hc1$order, hc2$order], 
          Rowv = FALSE, 
          Colv = FALSE, 
          cexRow = 0.3, 
          cexCol = 0.3)

@@

```{r local-local-pleio}
local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap()
```

```{r nonlocal-nonlocal-pleio}
nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

>>>>

---
title: "Chr11 hotspot analyses"
author: "Frederick Boehm"
date: "7/08/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
keller_mediator <- "Sat2"
library(hotspots)
fp <- paste0("../figures/Chr", hot_chr, "-")
knitr::opts_chunk$set(fig.path = fp)

@@

@@

```{r define_dri}
# need the index of the peak for every nonlocal trait
indices <- nonlocal_annot %>%
  mutate(marker_index = purrr::map_int(.x = marker.id, .f = function(x){which(names(map[[as.character(hot_chr)]]) == x)})) %>%
  dplyr::select(marker_index) %>%
  unlist() %>%
  as.integer()
```

@@

```{r tabulate, message=FALSE, warning = FALSE}
tib <- out %>%
  purrr::map(bind_rows) %>%
  bind_rows() %>%
  as_tibble() %>%
  rename(lod_without_med = lod_no_med, lod_with_med = lod_med) %>%
  mutate(lod_diff = lod_without_med - lod_with_med, lod_diff_proportion = lod_diff / lod_without_med) %>%
  mutate(local_gene_id = rep(colnames(hot_local), each = nnonlocal), nonlocal_gene_id = rep(colnames(hot_nonlocal), times = nlocal)) %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  left_join(nonlocal_annot, by = c("nonlocal_gene_id" = "annot.id")) %>%
  dplyr::select(symbol.x, symbol.y, lod_without_med, lod_with_med, lod_diff, lod_diff_proportion, local_gene_id, nonlocal_gene_id) %>%
  rename(local_symbol = symbol.x, nonlocal_symbol = symbol.y)
```

@@

```{r read_pleio_results}
pleio_file <- paste0("_cache/Chr", hot_chr, "_pleio.rds")
if (file.exists(pleio_file)) {mylist <- readRDS(pleio_file)} else {
  results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num)
  dir(results_dir) -> fns
  mylist <- list()
  for (i in 1:length(fns)){
    mylist[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(local_gene_id = stringr::str_split(fns[i], "_")[[1]][[3]], nonlocal_gene_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(local_gene_id, nonlocal_gene_id, lod, filename)
  }
  saveRDS(mylist, pleio_file)
}
```

@@

```{r plot_all}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05)
plotly::ggplotly(p)

@@

```{r, plotly_by_local, fig.height=ceiling(nlocal / 2), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

```{r, plotly_by_nonlocal, fig.height=ceiling(nnonlocal / 4), eval = FALSE}
p <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.1) + facet_wrap(. ~ nonlocal_symbol, ncol = 4, nrow = ceiling(nnonlocal / 4)) + theme(legend.position = "none")
#plotly::ggplotly(p)
```

@@

```{r define_foo}
foo <- mylist %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) 
```

```{r add_local_peak_positions}
foo %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  rename(local_peak_pos = pos, local_peak_lod = lod) %>%
  dplyr::select(- marker.id, - chrom, - strand, - biotype, - local_tx) %>%
  filter(local_peak_pos < hot_upper, local_peak_pos > hot_lower)

@@

```{r}
foo %>%
  left_join(local_annot2, by = c("local_gene_id" = "annot.id")) %>%
  rename(local_peak_pos = pos, local_peak_lod = lod) %>%
  dplyr::select(- marker.id, - chrom, - strand, - biotype, - local_tx) %>%
  filter(local_peak_pos < hot_upper, local_peak_pos > hot_lower) %>%
  dplyr::select(middle) %>% unlist() %>% range()

@@

```{r, hclust_pleio_stats}
bar <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, pleiotropy_lod) %>%
hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
```

@@

```{r, define_hld, eval = FALSE}
hld <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff)
plotly::plot_ly(as.data.frame(hld), z = as.data.frame(hld)$lod_diff, type = "heatmap")
```

@@

```{r define_hc_objects}
hc_lod_diff <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, lod_diff) %>%
  hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
hc_pleio <- foo %>%
  dplyr::select(nonlocal_gene_id, local_gene_id, pleiotropy_lod) %>%
  hotspots::tibble_to_matrix() %>%
  dist() %>%
  hclust() 
```

@@

```{r make_mylist}
med_vals <- 2 * (1:5)
pleio_vals <- 2 * (2:5)
mylist <- list()
for(i in 1:length(med_vals)){
  my_other_list <- list()
  for (j in 1:length(pleio_vals)){
    uniq_cts_nonlocal <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      dplyr::select(nonlocal_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_nonlocal_gene_id = n)
    uniq_cts <- foo %>% 
      mutate(med = lod_diff > med_vals[i], pleio = pleiotropy_lod <= pleio_vals[j]) %>%
      group_by(med, pleio) %>%
      dplyr::select(local_gene_id, med, pleio) %>%
      unique() %>%
      count() %>%
      rename(n_unique_local_gene_id = n) %>%
      left_join(uniq_cts_nonlocal, by = c("pleio", "med"))

@@

```{r read_pleio_results_local}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10 + 1)
dir(results_dir) -> fns
pleio_file_local <- paste0("_cache/Chr", hot_chr, "_pleio_local.rds")
if (file.exists(pleio_file_local)) {mylist_local <- readRDS(pleio_file_local)} else {
  mylist_local <- list()
  for (i in 1:length(fns)){
    mylist_local[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_local, pleio_file_local)
}

@@

```{r read_pleio_results_nonlocal}
results_dir <- paste0("~/Box Sync/attie/keller-hotspots/results/pvl-run-", run_num * 10)
dir(results_dir) -> fns
pleio_file_nonlocal <- paste0("_cache/Chr", hot_chr, "_pleio_nonlocal.rds")
if (file.exists(pleio_file_nonlocal)) {mylist_nonlocal <- readRDS(pleio_file_nonlocal)} else {
  mylist_nonlocal <- list()
  for (i in 1:length(fns)){
    mylist_nonlocal[[i]] <- read.table(file.path(results_dir, fns[i])) %>%
    as_tibble() %>%
    mutate(filename = fns[i]) %>%
    mutate(gene1_id = stringr::str_split(fns[i], "_")[[1]][[3]], 
           gene2_id = stringr::str_split(stringr::str_split(fns[i], "_")[[1]][[4]], ".txt")[[1]][[1]]) %>%
    filter(lod == max(lod), trace == "profile1") %>%
    dplyr::select(gene1_id, gene2_id, lod, filename)
  }
  saveRDS(mylist_nonlocal, pleio_file_nonlocal)
}
```

@@

```{r}
local_annot3 <- local_annot2 %>%
  dplyr::select(annot.id, symbol)
local_pleio <- mylist_local %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(local_annot3, by = c("gene1_id" = "annot.id")) %>%
  rename(gene1_symbol = symbol) %>%
  left_join(local_annot3, by = c("gene2_id" = "annot.id")) %>%
  rename(gene2_symbol = symbol)

nonlocal_annot3 <- nonlocal_annot %>%
  dplyr::select(annot.id, symbol)
nonlocal_pleio <- mylist_nonlocal %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  left_join(nonlocal_annot3, by = c("gene1_id" = "annot.id")) %>%
  rename(gene1_symbol = symbol) %>%
  left_join(nonlocal_annot3, by = c("gene2_id" = "annot.id")) %>%
  rename(gene2_symbol = symbol)

@@

```{r}
pleio_results_mat <- foo %>%
  dplyr::select(local_gene_id, nonlocal_gene_id, pleiotropy_lod, local_symbol, nonlocal_symbol) %>%
  rename(gene1_id = local_gene_id, 
         gene2_id = nonlocal_gene_id, 
         gene1_symbol = local_symbol,
         gene2_symbol = nonlocal_symbol
         ) %>%
  bind_rows(local_pleio, nonlocal_pleio) %>%
  hotspots::tibble_to_matrix(symmetric = TRUE)
```

@@

```{r heatmap.2}
pleio_mat <- foo %>%
  tibble_to_matrix() %>%
  t()
ld <- bar$lod_diff
idx1 <- match(x = bar$nonlocal_symbol, table = rownames(pleio_mat))
idx <- 1 + floor((ld * (ld > 0))[idx1])
cols[idx] -> indexed_colors
ic2 <- 1 + (ld[idx1] > mediation_threshold)
#indexed_colors[is.na(indexed_colors)] <- cols[8]
```

@@

```{r define_color}
hmcol <- colorRampPalette(brewer.pal(9, "GnBu"))(100)
```

@@

```{r, loddiff_clust}
foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as the stat of interest
  tibble_to_matrix() 
```

```{r, loddiffprop_clust}
foo %>%
  dplyr::select(1, 2, 5) %>% # choose lod_diff_proportion as stat of interest
  tibble_to_matrix() 
```

@@

```{r threshold_clust}
med_thresh <- 2
foomat <- foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
  apply(FUN = function(x) x <= med_thresh, X = foomat, MARGIN = 2) 
```

```{r}
foo %>%
  dplyr::select(1, 2, 4) %>% # choose lod_diff as stat of interest
  tibble_to_matrix()
```

@@

```{r}
bccc_out<- biclust(pleio_mat, method = BCCC())
c1 <- bicluster(pleio_mat, bccc_out, number = 1)
```

@@

```{r local-local-pleio}
local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3, symm = TRUE)

@@

```{r local-local-hclust}
l_l_hclust <- local_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  (function(x){x[is.null(x)] <- 0; return(x)}) %>%
  dist() %>%
  hclust()
l_l_hclust %>%  
  cutree(h = 40) %>% table()

l_l_hclust %>%
  rafalib::myplclust(cex = 0.4, lab.col = 1 + as.numeric(l_l_hclust$labels == keller_mediator))
```

```{r nonlocal-nonlocal-pleio}
nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3, symm = TRUE)
```

```{r nl-nl-hclust}
nl_nl_hclust <- nonlocal_pleio %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  dist() %>% 
  hclust()
plot(nl_nl_hclust, cex = 0.2)
nl_nl_hclust %>%
  cutree(h = 10) %>%
  table()
```

```{r rafalib-plot1}
# make color labels for dendro plot
precols <- tibble(nonlocal_symbol = nl_nl_hclust$labels) %>%
  left_join(bar) %>% # bar has local_symbol set to keller_mediator
  dplyr::arrange(match(x = nonlocal_symbol, table = nl_nl_hclust$labels))
# check ordering of nonlocal_symbol against nl_nl_hclust$labels
# IT'S THE SAME, but only after including the call to dplyr::arrange()

cols <- 1 + (precols$lod_diff > 1.5)
# dendro plot
nl_nl_hclust %>%
  rafalib::myplclust(cex = 0.3, lab.col = cols)
```

## Pleiotropy test results for *all* trait pairs

```{r all-pleio}
foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  d3heatmap(cexRow = 0.2, cexCol = 0.2)
```

```{r, all-all-hclust}
all_all_hclust <- foo %>%
  dplyr::select(9, 10, 3, 8, 1, 2) %>%
  rename(gene1_id = nonlocal_gene_id,
         gene2_id = local_gene_id,
         gene1_symbol = nonlocal_symbol, 
         gene2_symbol = local_symbol
         ) %>%
  bind_rows(local_pleio) %>%
  bind_rows(nonlocal_pleio) %>%
  dplyr::select(5, 6, 3) %>%
  tibble_to_matrix(symmetric = TRUE) %>%
  dist() %>%
  hclust()
```

```{r rafalib-plot2}
cols <- 1 + (all_all_hclust$labels %in% bar$nonlocal_symbol)
cols[all_all_hclust$labels == keller_mediator] <- 3
# dendro plot
all_all_hclust %>%
  rafalib::myplclust(cex = 0.2, 
                     lab.col = cols, 
                     main = paste0("Chr", 
                                   hot_chr, 
                                   " dendrogram"
                                   ), 
                     sub = "pleiotropy test statistics"
                       )

@@

## Mediation (LOD diff) results (truncated at zero) for local-nonlocal pairs

```{r med-trunc-heat}
foo %>%
  dplyr::select(1, 2, 4) %>%
  mutate(lod_diff_trunc = lod_diff * (lod_diff > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```

## Mediation (LOD diff proportion) results (truncated at zero) for local-nonlocal pairs

```{r med-prop-trunc-heat}
foo %>%
  dplyr::select(1, 2, 5) %>%
  mutate(lod_diff_prop_trunc = lod_diff_proportion * (lod_diff_proportion > 0)) %>%
  dplyr::select(-3) %>%
  tibble_to_matrix(symmetric = FALSE) %>%
  d3heatmap(cexRow = 0.3, cexCol = 0.3)
```
